\cvsection{Experience}
\begin{cventries}
\cventry{Contract Scala Developer}{Cloud Technologies S.A.}{Warsaw}{01.2018 --- now}{
Development and maintenance of Real-Time Bidding (RTB) client platform. Developing the internal product, hosted on private (100+) servers. The solution is deployed in a cluster for both high availability and maximum throughput (~200k req/s) with lowest response time possible~(<100ms). Working closely with analysts team and media planers, creating product's improvement strategies and having a real impact on chosen solutions.
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Back-end development using Scala}
	\item{Building scalable and efficient asynchronous solutions}
	\item{Managing CI/CD pipeline using Jenkins}
	\item{Managing production environment and deployment using Ansible}
	\item{Logs monitoring and system statistics with ELK stack}
	\item{System monitoring using Grafana \& Graphite}
\end{itemize}
\textbf{Used technologies}: Scala, Java, Cassandra, Kafka, Aerospike, Memcache, Redis, Ansible, Guice, Spring Boot, Apache Spark, Hive, sbt, maven, Jenkins, Git, Logstash, ElasticSearch, Kibana, Grafana, Graphite.
}


\cventry{Contract Scala Developer}{QuintilesIMS}{Warsaw}{03.2017 --- 12.2017}{
Developing data processing Spark solution deployed on a private cloud data centre based on Cloudera Hadoop Stack. Creating data processing pipelines for batch processing of big volume sources. 
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Back-end development using Scala with Apache Spark}
	\item{Introduced to functional Scala libraries: Cats, Shapeless, Circe, Monix, Akka}
	\item{Managing CI/CD pipeline using Jenkins}
	\item{Preparing production environment and deployment automation using Ansible}
	\item{Logs monitoring with ELK stack}
	\item{Scrum work environment}
\end{itemize}
\textbf{Used technologies}: Scala, Apache Spark, Hadoop, YARN, HDFS, sbt, Jenkins, Ansible, Git, Logstash, ElasticSearch, Kibana.
}

\cventry{Java/Scala Developer}{DOT Systems Sp. z o.o.}{Warsaw}{07.2015 --- 02.2017}{
Working in the development and maintenance team in telecommunications industry for clients based in Middle East. Development of high-traffic capable web applications.
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Back-end product maintenance using Java 8, Jersey, Guice and EclipseLink}
	\item{Back-end development using Scala and Play Framework}
	\item{Front-end development using Javascript, AngularJS, LESS/SASS, based on Grunt/Gulp build tool.}
	\item{Introduced to functional programming \& streams}
	\item{Automatic roll-outs using Ansible}
	\item{Managing of internal Atlassian (Jira/Confluence/BitBucket) and Jenkins environments using Vagrant VMs}
\end{itemize}
\textbf{Back-end technologies}: Java 8, Scala, Tomcat, Play Framework, Guice, EclipseLink, sbt, Maven, Jenkins, Ansible, Git, Vagrant, NGiNX.
\\\textbf{Front-end technologies}: JavaScript, TypeScript, AngularJS, React, Grunt, Gulp, Webpack, CSS, LESS, SASS.
}

\cventry{Software Engineering Associate}{Accenture}{Lodz}{10.2012 --- 06.2014}{
Part of eCommerce Hybris Core Development team.
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Back-end development of hybris-based platform using Spring Framework, Hibernate/JPA}
	\item{Front-end development using JSP, JavaScript and CSS}
	\item{Agile work environment}
	\item{Part of multinational projects, with partners in: Italy, Switzerland, United Kingdom and United States of America}
\end{itemize}
\textbf{Back-end technologies}: Java, Spring Framework, Hibernate, JPA, Hybris, Tomcat.
\\\textbf{Front-end technologies}: JavaScript, JSP, CSS.
}

\cventry{Intern}{Accenture}{Lodz}{07.2012 --- 09.2012}{
Part of an internal project that aimed to automate application process during job fairs.
\\ \textbf{Key responsibilities}:
\begin{itemize}
	\item{Preparation of demo environment}
	\item{Code development}
	\item{Preparing technical documentation}
\end{itemize}
\textbf{Back-end technologies}: Java, ESP 3, EclipseLink, GlassFish.
\\\textbf{Front-end technologies}: PrimeFaces, JSF, CSS.
}


\end{cventries}
